Getting start

### 2023-05-25 inst/gitbook/01_getting_started.Rmd
Updated gitbook for v0.2

## An illustrative example: mammals disparity through the K-Pg extinction {kpgexample}

@@

They use a dataset from @BeckLee that is a discrete morphological space containing the ordination of the around 400 morphological characters for 50 species and estimated for their 49 descendants into an ordinated shapespace of 99 elements and 97 dimensions.

@@

```{r}
## Simulate the tree and traits with a random extinction event
sim_rand_extinction <- treats(
                   traits     = my_traits,
                   bd.params  = est_params,
                   stop.rule  = stop_rule,
                   events     = random_extinction,
                   null.error = 100,
                   replicates = 50)

>>>>

## An illustrative example: mammals disparity through the K-Pg extinction {#kpgexample}

@@

They use a dataset from @beckancient2014 that is a discrete morphological space containing the ordination of the around 400 morphological characters for 50 species and estimated for their 49 descendants into an ordinated shapespace of 99 elements and 97 dimensions.

@@

```{r, message = FALSE}
## Simulate the tree and traits with a random extinction event
sim_rand_extinction <- treats(
                   traits     = my_traits,
                   bd.params  = est_params,
                   stop.rule  = stop_rule,
                   events     = random_extinction,
                   null.error = 100,
                   replicates = 50)
